Bioverse: Origins of Life

### 2024-03-01 src/tex/ms.tex
argue for O2

\subsection{Exoplanet survey simulations}
\todo[inline]{biosignatures: Focus on molecular Oxygen? Excess Methane? \citep[e.g.,][]{Seeburger2023}}
% detecting methanogenic life: Sandora2020, Wang2018,
A commonly discussed biosignature is molecular Oxygen (O$_2$), which on Earth emerged as a byproduct of photosynthesis during the Proterozoic era.
While not the only atmospheric species discussed as a signature for planetary life CITE, we focused on O$_2$ as a representative biosignature for our spectroscopic survey simulations.

>>>>

\subsection{Exoplanet survey simulations}
\todo[inline]{biosignatures: Focus on molecular Oxygen? Excess Methane? \citep[e.g.,][]{Seeburger2023}}
% detecting methanogenic life: Sandora2020, Wang2018,
A commonly discussed biosignature is molecular Oxygen (O$_2$), which on Earth emerged as a byproduct of photosynthesis during the Proterozoic era.
No individual component of an atmosphere has been identified as a reliable biosignature in isolation~\citep{Seager2016}, and the detection of Oxygen alone will certainly not be sufficient to confirm the presence of life.
Nevertheless, we focus here on detecting this key absorber as it represents the general inherent observational challenges and trends.
